A dynamic programming algorithm to assess the reliability of inferences from network enrichment analysis

### 2018-05-03 doc/genesetdp.tex
Not sure why this is needed.
Replacing lost header
readded documment class
new plots
text

\documentclass[a4paper,american]{lipics-v2016}
%\usepackage[USenglish]{babel}
%\usepackage{microtype}
\bibliographystyle{plainurl}
\title{A dynamic programming algorithm to assess the reliability of inferences from network enrichment analysis}
\titlerunning{Dynamic Programming for Inferences from Network Enrichment Analysis} %optional, in case that the title is too long; the running title should fit into the top page column

@@

The quality of the inferences from NEA has previously been assessed by Monte Carlo-simulations that investigates the scores distribution when evaluating the query set using random networks.

@@

\begin{figure}[htb]
		\begin{center}
				\includegraphics[scale=0.8]{figures/F1_score_distribuition.png}
		\end{center}
%FIXME: Do not use figure numbers in their file name, this creates havoc if you want to reorganize them later
  \caption{{\bf Score distribution of a query size of 25 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

\begin{figure}[htb]
		\begin{center}
				\includegraphics[scale=0.8]{figures/F2_calibration.png}
		\end{center}

@@

>>>>

\documentclass[a4paper,american]{lipics-v2016}
% \usepackage[USenglish]{babel}
% \usepackage{microtype}
\bibliographystyle{plainurl}
\title{A dynamic programming algorithm to assess the reliability of inferences from network enrichment analysis}
\titlerunning{Dynamic Programming for Inferences from Network Enrichment Analysis} %optional, in case that the title is too long; the running title should fit into the top page column

@@

FIXME: Review the mentioned methods. Particularly which null models do they use?

The quality of the inferences from NEA has previously been assessed by Monte Carlo-simulations that investigates the scores distribution when evaluating the query set using random networks which are generated using methods with varying degrees of topological conservation.

Since these methods of network randomization are not completely random, they introduce bias in the statistics that may or may not be desired, as the set of random networks is much larger than the ones of random networks that retain a certain topological characteristic. And the somewhat inaccessible process of so randomising networks produces statistics that are equaly hard to interpret. FIXME: Should this be in the dicussion?

@@

\begin{figure}[htb]
		\begin{center}
				\includegraphics[scale=0.8]{figures/score_distribuition.png}
		\end{center}
%FIXME: Do not use figure numbers in their file name, this creates havoc if you want to reorganize them later
  \caption{{\bf Score distribution of a query size of 25 genes against the ``Glycolysis/Gluconeogenesis'' pathway.} GeneSetDP enables us to calculate the full score distribution for a query of a given size, $Q$, i.e. how many ways one can reach a certain score when adding up the scores for $Q$ genes.}
  \label{fig:score_dist}
\end{figure}

@@

\begin{figure}[htb]
		\begin{center}
				\includegraphics[scale=0.8]{figures/calibration.png}
		\end{center}

@@

FIXME: Is it ok to state the method is more accurate if we are testing it agains a different null hypothesis

FIXME: What about:
